---
title: "Create a Study Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create a Study Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Use `insertStructure()` to set up a new OMOP study package with common folders,
starter scripts, tests, and package dependencies.

## Before you start

Create an empty R package and make sure you have internet access. The setup
installs the standard study-package dependencies.

## 1. Create an empty package

Create a package with `usethis`, or use **File > New Project** in RStudio.

```{r, eval=FALSE}
usethis::create_package(
  path = "~/P1C1001"
)

```

## 2. Initialize the environment

Inside the new package, initialize `renv` and install `studyGenerics`.

```{r, eval=FALSE}
renv::init()

renv::install("mi-erasmusmc/studyGenerics")

```

## 3. Insert the study structure

Run `insertStructure()` from the package directory. `n_obj` sets the number of
objective scripts to create.

```{r, eval=FALSE}
studyGenerics::insertStructure(
  path = ".",
  n_obj = 3
)

```

The package will include:

```
studyPackage/
├── R/
│   ├── createCohorts.R
│   ├── runStudy.R
│   ├── runDiagnostics.R
│   ├── utils.R
│   ├── globals.R
│   ├── merge.R
│   └── objective1.R, ..., objective<n_obj>.R
├── inst/
│   ├── cohorts/
│   └── concept_sets/
├── extras/
│   ├── CodeToRun.R
│   └── pullConceptSetsFromAtlas.R
├── man/
├── tests/
│   └── testthat/test-*.R
├── LICENSE.md
├── NEWS.md
└── README.Rmd
```

## 4. Next steps

Add concept sets to `inst/concept_sets/`, develop the study code in `R/`, then
generate documentation with `devtools::document()` and check the package with
`devtools::check()`.
