---
title: "Inserting a New Package Structure"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Create an empty project

First, create a new empty project for your new study package with the package use this or from the menu in RStudio (Menu > File > New Project). The package will open a new instance of Positron or Rstudio. 

```{r, eval=FALSE}
library(usethis)

usethis::create_package(
  path = "~/P1C1001"
  )

```

## Initiate an environment

Inside the new study package use `renv` to initialise a new environment to start installing packages and install `studyGenerics`

```{r, eval=FALSE}
library(renv)

renv::init()

renv::install("mi-erasmusmc/studyGenerics")

```

## Insert the structure

Finally, use the function `studyGenerics::insertStructure` to create a common configuration of packages and files to start developing a study package. You can use the parameter `n_obj` to define the number of objectives in your study. This will create a file to write a script for each objective in the /R folder. 

```{r, eval=FALSE}
library(studyGenerics)

studyGenerics::insertStructure(
  path = ".", # Default to create the study structure in the package you are currently in
  n_obj = 3 # Default 3, in number.
)

```